MLExplain

### 2018-05-23 paper.tex
Refactor pour faire tenir le code sur 80 colonnes

% Expliquer que JSExplain est écrit en OCaml et compilé vers JavaScript pour être intégré dans
% la page web qui va avec

JSExplain needs its own OCaml to JavaScript compiler in order to place the calls to
\verb|log_event| which is the tracing function. This function is also used to get the location
of the different syntactical objects in the source file in order to produce code highlighting in
JSExplain's interface.

>>>>

% Référence pour coq ?
JSExplain was first written in Coq. OCaml code has been extracted from the Coq
source and is now the primary source code. The interpreter is compiled into
JavaScript in order to use it within a web page. For this reason, the project
embeds a homemade OCaml-to-JavaScript compiler.

JSExplain also needs its own OCaml to JavaScript compiler in order to place the
calls to \verb|log_event| which is the tracing function. This function is also
used to get the location of the different syntactical objects in the source
file in order to produce code highlighting in JSExplain's interface.
